NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-08-26 paper/Chapters/Chapter2.tex
grammarly checked again

\begin{itemize}
	\item $ U_{ijk} $ represents the response of carbohydrate eating (one of the following: not eating any food, $< 50\%$ of the energy, or $\geqslant 50\%$ of the energy) on the $i$th day of the survey ($i \in (1,2,3,4)$) in $j$th individual at the $k$th time slot of the day ($k \in (1, 2, 3, \cdots, 7)$);
	\item $G_{ij}$ denotes the latent class membership for $j$th individuals on $i$th day of the survey, the total number of day-level latent class is $T$;
%	\item A specific latent class is referred to as $t$, and the total number of level 1 latent classes is denoted by $T$;
	\item $P(U_{ijk} = s_k|C_{ij} = t)$ is the probability of a specific response pattern, conditional on membership in latent class $t$.
\end{itemize}

@@

\begin{itemize}
	\item $CB_j$ is the individual-level latent class membership for the $j$th individual;
	\item $\gamma_{tm}$ is day-level and individual-level indicators. 
\end{itemize}

>>>>

\begin{itemize}
	\item $ U_{ijk} $ represents the response of carbohydrate eating (one of the following: not eating any food, $< 50\%$ of the energy, or $\geqslant 50\%$ of the energy) on the $i$th day of the survey ($i \in (1,2,3,4)$) in $j$th individual at the $k$th time slot of the day ($k \in (1, 2, 3, \cdots, 7)$);
	\item $G_{ij}$ denotes the latent class membership for $j$th individuals on the $i$th day of the survey, the total number of day-level latent class is $T$;
%	\item A specific latent class is referred to as $t$, and the total number of level 1 latent classes is denoted by $T$;
	\item $P(U_{ijk} = s_k|C_{ij} = t)$ is the probability of a specific response pattern, conditional on membership in latent class $t$.
\end{itemize}

@@

\begin{itemize}
	\item $CB_j$ is the individual-level latent class membership for the $j$th individual;
	\item $\gamma_{tm}$ is the day-level and individual-level indicators. 
\end{itemize}

### 2018-08-26 paper/Chapters/Chapter3.tex
grammarly checked again

Class 2 days \textbf{(Figure \ref{fig:level1}-B)} were named as "low percentage carbohydrate day" because first of all, in these days the probability of participants skipping breakfast was 0.45. And after 9 am, within these days, the probability of having low carbohydrate contained food (carbohydrate contributed $<$ 50\% of total energy intake), was always higher than having high carbohydrate contained food (carbohydrate contributed $\geqslant$ 50\% of total energy intake). In class 2 days, participants also turned to have morning snacks (with probability of only 0.079 of \textbf{not} eating any food and similar probabilities of having either high or low carbohydrate contained food). This phenomenon may also be interpreted as having a long and late breakfast (brunch) in these mornings. The probability of \textbf{not} eating any food was the lowest for low carbohydrate days during the midnight time slot (10 pm to 6 am), with a probability of 0.590 compared with 0.680 and 0.751 in class 1 and class 3 days, respectively.

@@

The social-demographic characteristics of the UK adults according to their individual level latent class membership are shown in \textbf{Table \ref{tab:Level2tab1}}. Moderate carbohydrate eaters were relatively younger (\textit{p} < 0.001). Gender distribution across the three types of carbohydrate eaters was fairly even (\textit{p} = 0.119). The distribution of the carbohydrate eater types turned out to be changing with the year of survey. Low carbohydrate eaters represented 32.5\% of the population in the first year of survey but later dropped to lower than 30\% (lowest in the third year, 22.6\%) until the most recent year. The proportion of high carbohydrate eaters increased from 41.2\% to the highest (50.6\%) in the second year, but then started to decline to 38.4\% in the 8th year of survey (\textit{p} = 0.015). There was no evidence of any difference in employment status across three types of carbohydrate eaters. However, strong evidence suggested that high carbohydrate eaters had the highest proportion (61.3\%) of living with partner (\textit{p} < 0.001); moderate carbohydrate eaters had the lowest average income (27180.8 \textsterling/year), highest proportion of non-white population (20.5\%), and lower education level (23.3\% with degree of higher education) compared with either low or high carbohydrate eaters.

@@

\textbf{Table \ref{tab:tab1BMI}} shows the characteristics for participants according to their obesity status stratified by sex. The survey design-weighted prevalence for being overweight and obese in the UK adults were estimated to be 43.4\% and 25.7\% in men, and 30.9\% and 27.4\% in women. Obviously, abdominal obesity (WC) increased significantly with the elevated BMI level in both men and women. Overweight or obese participants were older, having lower total energy intake and lower carbohydrate intake compared with normal weight men and women (\textit{p} < 0.001). Moreover, education

>>>>

Class 2 days \textbf{(Figure \ref{fig:level1}-B)} were named as "low percentage carbohydrate day" because first of all, in these days the probability of participants skipping breakfast was 0.45. And after 9 am, within these days, the probability of having low carbohydrate contained food (carbohydrate contributed $<$ 50\% of total energy intake), was always higher than having high carbohydrate contained food (carbohydrate contributed $\geqslant$ 50\% of total energy intake). In class 2 days, participants also turned to have morning snacks (with a probability of only 0.079 of \textbf{not} eating any food and similar probabilities of having either high or low carbohydrate contained food). This phenomenon may also be interpreted as having a long and late breakfast (brunch) in these mornings. The probability of \textbf{not} eating any food was the lowest for low carbohydrate days during the midnight time slot (10 pm to 6 am), with a probability of 0.590 compared with 0.680 and 0.751 in class 1 and class 3 days, respectively.

@@

The social-demographic characteristics of the UK adults according to their individual level latent class membership are shown in \textbf{Table \ref{tab:Level2tab1}}. Moderate carbohydrate eaters were relatively younger (\textit{p} < 0.001). Gender distribution across the three types of carbohydrate eaters was fairly even (\textit{p} = 0.119). The distribution of the carbohydrate eater types turned out to be changing with the year of survey. Low carbohydrate eaters represented 32.5\% of the population in the first year of the survey but later dropped to lower than 30\% (lowest in the third year, 22.6\%) until the most recent year. The proportion of high carbohydrate eaters increased from 41.2\% to the highest (50.6\%) in the second year, but then started to decline to 38.4\% in the 8th year of survey (\textit{p} = 0.015). There was no evidence of any difference in employment status across three types of carbohydrate eaters. However, strong evidence suggested that high carbohydrate eaters had the highest proportion (61.3\%) of living with partner (\textit{p} < 0.001); moderate carbohydrate eaters had the lowest average income (27180.8 \textsterling/year), highest proportion of non-white population (20.5\%), and lower education level (23.3\% with degree of higher education) compared with either low or high carbohydrate eaters.

@@

\textbf{Table \ref{tab:tab1BMI}} shows the characteristics of participants according to their obesity status stratified by sex. The survey design-weighted prevalence for being overweight and obese in the UK adults were estimated to be 43.4\% and 25.7\% in men, and 30.9\% and 27.4\% in women. Obviously, abdominal obesity (WC) increased significantly with the elevated BMI level in both men and women. Overweight or obese participants were older, having lower total energy intake and lower carbohydrate intake compared with normal weight men and women (\textit{p} < 0.001). Moreover, education

### 2018-08-26 paper/main.tex
grammarly checked again

\large \textbf{Submitted in part fulfillment of the requirements\\ for the degree of \degreename}\\[0.3cm] % University requirement text
%\textit{in the}\\[0.4cm]
\groupname\\\deptname\\[1.8cm] % Research group name and department name

@@

\begin{itemize}
\item This work was done wholly while in candidature for a MSc degree in Medical Statistics at London School of Hygiene and Tropical Medicine.
\item No part of this thesis has previously been submitted for a degree or any other qualification at London School of Hygiene and Tropical Medicine or any other institution.
\item Where I have consulted the published work of others, this is always clearly attributed.
\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
\item I have acknowledged all main sources of help.
\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
\end{itemize}

@@

\textbf{Conclusions:}
Contrary to the expectation, profiles of high-carb eaters seemed to be healthier among three types of carb eaters. Low-carb eaters probably followed the diet out of health purposes but they may have chosen fat or alcohol as replacements of carb, which could probably be a concern from a public health point of view. Whether these circadian carb-eating patterns are associated with changes of blood pressure and/or obesity longitudinally should be further investigated.

@@

\textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
\textbf{A1c} & Haemoglobin \textbf{A1c}: Glycated haemoglobin \\
%\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
\textbf{BMI} & \textbf{B}ody \textbf{M}ass \textbf{I}ndex \\
%\textbf{cAIC} & \textbf{c}onsistent \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
\textbf{BIC} & \textbf{B}ayesian \textbf{I}information \textbf{C}riterion \\
\textbf{CI}  & \textbf{C}onfidence \textbf{I}nterval \\
\textbf{DM}  & \textbf{D}iabetes \textbf{M}ellitus \\
%\textbf{EM}  & \textbf{E}xpectation \textbf{M}aximazation  \\
\textbf{FSA} & \textbf{F}ood \textbf{S}tandards \textbf{A}gency  \\
\textbf{HDL} & \textbf{H}igh \textbf{D}ensity \textbf{L}ipoprotein cholesterol \\
\textbf{LDL} & \textbf{L}ow \textbf{D}ensity \textbf{L}ipoprotein cholesterol \\
\textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
\textbf{LCGA} & \textbf{L}atent \textbf{C}lass \textbf{G}rowth \textbf{A}nalysis \\
\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
\textbf{MAFF} & \textbf{M}inistry of \textbf{A}griculture, \textbf{F}isheries and \textbf{F}ood \\
%\textbf{MAR} & \textbf{M}issing \textbf{A}t \textbf{R}andom \\
%\textbf{MCAR} & \textbf{M}issing \textbf{C}ompletely \textbf{A}t \textbf{R}andom \\
\textbf{MLCA} & \textbf{M}ultilevel \textbf{L}atent \textbf{C}lass \textbf{A}nalysis \\
%\textbf{MNAR} & \textbf{M}issing \textbf{N}ot \textbf{A}t \textbf{R}andom \\
\textbf{ML} & \textbf{M}aximum \textbf{L}ikelihood \\
\textbf{NDNS} & the \textbf{N}ational \textbf{D}iet and \textbf{N}utrition \textbf{S}urvey \\
\textbf{OR} & \textbf{O}dds \textbf{R}atio \\
\textbf{PHE} & \textbf{P}ublic \textbf{H}ealth \textbf{E}ngland  \\
\textbf{PSUs} & \textbf{P}rimary \textbf{S}ampling \textbf{U}nits \\
\textbf{RMLCA} & \textbf{R}epeated \textbf{M}easures \textbf{LCA} \\
\textbf{TC} & \textbf{T}otal \textbf{C}holesterol \\
\textbf{TG} & \textbf{T}ri\textbf{g}lycerides \\
\textbf{WC}   & \textbf{W}aist \textbf{C}ircumference \\
\end{abbreviations}

>>>>

\large \textbf{Submitted in partial fulfillment of the requirements\\ for the degree of \degreename}\\[0.3cm] % University requirement text
%\textit{in the}\\[0.4cm]
\groupname\\\deptname\\[1.8cm] % Research group name and department name

@@

\begin{itemize}
\item This work was done wholly while in candidature for an MSc degree in Medical Statistics at London School of Hygiene and Tropical Medicine.
\item No part of this thesis has previously been submitted for a degree or any other qualification at London School of Hygiene and Tropical Medicine or any other institution.
\item Where I have consulted the published work of others, this is always clearly attributed.
\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
\item I have acknowledged all main sources of help.
\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
\end{itemize}

@@

\textbf{Conclusions:}
Contrary to the expectation, profiles of high-carb eaters seemed to be healthier among three types of carb eaters. Low-carb eaters probably followed the diet out of health purposes but they may have chosen fat or alcohol as replacements of carb, which could probably be a concern from a public health point of view. Whether these circadian carb-eating patterns are associated with changes in blood pressure and/or obesity longitudinally should be further investigated.

@@

\textbf{AIC} & \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
\textbf{A1c} & Haemoglobin \textbf{A1c}: Glycated haemoglobin \\
%\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
\textbf{BMI} & \textbf{B}ody \textbf{M}ass \textbf{I}ndex \\
%\textbf{cAIC} & \textbf{c}onsistent \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
\textbf{BIC} & \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
\textbf{CI}  & \textbf{C}onfidence \textbf{I}nterval \\
\textbf{DM}  & \textbf{D}iabetes \textbf{M}ellitus \\
%\textbf{EM}  & \textbf{E}xpectation \textbf{M}aximazation  \\
\textbf{FSA} & \textbf{F}ood \textbf{S}tandards \textbf{A}gency  \\
\textbf{HDL} & \textbf{H}igh \textbf{D}ensity \textbf{L}ipoprotein cholesterol \\
\textbf{LDL} & \textbf{L}ow \textbf{D}ensity \textbf{L}ipoprotein cholesterol \\
\textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
\textbf{LCGA} & \textbf{L}atent \textbf{C}lass \textbf{G}rowth \textbf{A}nalysis \\
\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
\textbf{MAFF} & \textbf{M}inistry of \textbf{A}griculture, \textbf{F}isheries and \textbf{F}ood \\
%\textbf{MAR} & \textbf{M}issing \textbf{A}t \textbf{R}andom \\
%\textbf{MCAR} & \textbf{M}issing \textbf{C}ompletely \textbf{A}t \textbf{R}andom \\
\textbf{MLCA} & \textbf{M}ultilevel \textbf{L}atent \textbf{C}lass \textbf{A}nalysis \\
%\textbf{MNAR} & \textbf{M}issing \textbf{N}ot \textbf{A}t \textbf{R}andom \\
\textbf{ML} & \textbf{M}aximum \textbf{L}ikelihood \\
\textbf{NDNS} & the \textbf{N}ational \textbf{D}iet and \textbf{N}utrition \textbf{S}urvey \\
\textbf{OR} & \textbf{O}dds \textbf{R}atio \\
\textbf{PHE} & \textbf{P}ublic \textbf{H}ealth \textbf{E}ngland  \\
\textbf{PSUs} & \textbf{P}rimary \textbf{S}ampling \textbf{U}nits \\
\textbf{RMLCA} & \textbf{R}epeated \textbf{M}easures \textbf{LCA} \\
\textbf{TC} & \textbf{T}otal \textbf{C}holesterol \\
\textbf{TG} & \textbf{T}ri\textbf{g}lycerides \\
\textbf{WC}   & \textbf{W}aist \textbf{C}ircumference \\
\end{abbreviations}
